---
title: "linear model from Web"
author: "Cadence Gorden"
date: "Fall 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=ARM,x=SIMS))
basicNN + geom_point() + geom_lm()
```

This scatter plot shows us that it is a positive linear relationship. The fit line is going up to the right. 

### Numerical results

```{r}
cor(SIMS ~ ARM,data=data)
```

The correlation between SIMS and ARM is o.68 which means it is a positive correlation. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

#### Predict at target point

```{r}
mydat<- data.frame(GRIP = 94, ARM =88)
```

```{r}
predict(model.1,mydat,interval = "prediction")
```

We can see that the prediction here is 0.70, the lower is -1.72, and the upper is 3.13. 

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=ARM,x=SIMS))
basicNN + geom_point() + geom_lm()
```
  

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
basicNN <- ggplot(data,aes(y=GRIP,x=SIMS))
basicNN + geom_point() + geom_lm()
```

This is a positive linear fit with the line going right and up for GRIP and SIMS. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The numerical data shows us that the linear correltation is 0l63 which is a positive correlation. 

### Inferential  (Build model.2)
  
```{r}
model.1 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```


#### predict model.2 at target point

```{r}
mydat<- data.frame(GRIP = 94, ARM =88)
```

```{r}
predict(model.1,mydat,interval = "prediction")
```

The prediction here is -0.536, the low is -13.107, and the upper is 2.035.

#### now add the model fit to our plot for model.2

```{r}
basicNN <- ggplot(data,aes(y=GRIP,x=SIMS))
basicNN + geom_point() + geom_lm()
```


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation number according to the numerical results is 0.732 so this is a positive linear correlaton.
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

